The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-06-02 paper/ms.tex
minor text update

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf RMS vs mag for CDIPS light curves.}
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

First, to identify periodic transit-like signals, we used 
\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
The algorithm is the same as the canonical box least-squares
\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
template is used  for a marginal improvement of the detection efficiency.
In addition, the search grids in the \texttt{tls} 
implementation\footnote{\url{https://github.com/hippke/tls}} are slightly more 
efficient than in most BLS implementations, since it uses the 
cubic-in-frequency sampling advocated for by \citet{ofir_optimizing_2014}, 
rather than standard linear-in-frequency sampling.
During the period search, we rejected $6\,{\rm hours}$ at the
beginning and end of each spacecraft orbit, to mitigate the presence
of correlated red noise in the results.
This shrinks the data volume by about 5\%, but also lowers the number
of systematic false positives in subsequent vetting.
We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 
have additional periodicity information.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation of light curves vs catalog
  TESS-band magnitude for CDIPS light curves.}  Faint stars in heavily
  crowded regions have bright neighbors which drive their light curve
  scatter below the expected noise limits.
		\label{fig:rms_vs_mag}
	}
\end{figure}

@@

First, to identify periodic transit-like signals, we used 
\citet{hippke_TLS_2019}'s transit least-squares (TLS) tool.
The algorithm is the same as the canonical box least-squares
\citep{kovacs_box-fitting_2002}, except in place of a box template, a transit 
template is used  for a marginal improvement of the detection efficiency.
In addition, the search grids in \texttt{tls} 
\footnote{\url{https://github.com/hippke/tls}} are slightly more 
efficient than in most BLS implementations, since \texttt{tls} uses the 
cubic-in-frequency sampling advocated by \citet{ofir_optimizing_2014}, 
rather than standard linear-in-frequency sampling.
During the period search, we rejected $6\,{\rm hours}$ at the
beginning and end of each spacecraft orbit, to mitigate the presence
of correlated red noise in the results.
This shrinks the data volume by about 5\%, but also lowers the number
of systematic false positives in subsequent vetting.
Our grids typically consisted of about 25 different durations, and
about 2500 periods between 0.5 and 11 days.
We also ran a generalized Lomb-Scargle periodogram (CITE), simply to 
have additional periodicity information.
